Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-18 chi2012.tex
a  few more

\subsubsection{Results}
Table \ref{tbl:prestudy2} displays the raw results of the process just described.  A number of features were quite striking about the data. First, while most of the data records were small and relatively simple, nearly one in each category produced substantially more complex records than the rest; in particular, amazon, soundcloud, Twitter and Weather Underground stood out in their respective categories.

@@

The second thing we find is that equivalent properties were sometimes, though only rarely, given the same name.  Thus, terminological heterogeneity was prevalent across data records we observed.  Structural heterogeneity, however, was comparatively rare, with the most common case (comprising a majority of the cases) occurring

>>>>

\subsubsection{Results}
Table \ref{tbl:prestudy2} displays the raw results of the process just described.  A number of features were quite striking about the data. First, while most of the data records were small and relatively simple, nearly one in each category produced substantially more complex records than the rest; in particular, Amazon, Soundcloud, Twitter and Weather Underground stood out in their respective categories.

@@

The second finding is that equivalent properties were sometimes, though only rarely, given the same name.  Thus, terminological heterogeneity was prevalent across data records we observed.  Structural heterogeneity, however, was comparatively rare, with the most common case being that a leaf property on one record was modeled as a subtree in a target schema.
